Mitigating Interest Flooding DDoS Attacks in NDN

### 2013-01-11 01-intro.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

We conduct simulation-based evaluations to quantify the effectiveness of our proposed attack mitigation algorithms (Section~\ref{sec:evaluation}).
%% based on trivial small-scale and Internet-like larger-scale topologies.
The results show a great potential of one of the designed algorithms (dynamic limits, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
\todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}

>>>>

We conduct simulation-based evaluations to quantify the effectiveness of our proposed attack mitigation algorithms (Section~\ref{sec:evaluation}).
%% based on trivial small-scale and Internet-like larger-scale topologies.
The results show a great potential of one of the designed algorithms (satisfaction-based pushback, Section~\ref{sec:dynamic limits}), where the attack traffic can be effectively localized near the attacker himself.
\todo{LZ: I did not modify this last paragraph; need to see the rest of the paper first.}

### 2013-01-11 07-discussion.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

The attack mitigation methods studied in this paper provide ways to eliminate network congestion and router overload problems caused by junk Interest flooding (Section~\ref{sec:interest flooding}), but unfortunately not without inducing some new problems.
In particular, during an ongoing attack, a number of legitimate Interests successfully forwarded towards the Data producer can be substantially larger in unprotected network, then in the network that implements an Interest mitigation algorithm.  
This is simply because an unprotected network allows clients to pump more packets and does not impose any artificial restrictions on packet forwarding.
Therefore, unless a mitigation algorithm uses some form of intelligence (e.g., statistics for Interest satisfiability), a smaller scale flooding attack can cause greater damage to the service quality (recall service quality curves for physical limits in small-scale and larger-scale evaluations, Fig.~\ref{fig:small-scale} and Fig.~\ref{fig:large-scale}).

@@

In the definition of the Interests flooding attack we explicitly stated that an attack is carried using junk Interets, which obviously gives us a clear distinction between ``good'' and ``bad'' Interests.
A curious reader may ask us a valid question: what would happen if an adversary doing something else, e.g., sending sends only ``legitimate'' Interests or intermix them with junk Interests?
Although a complete investigation of this problem deserves a separate study, we anticipate that the problem may not be as severe as it seems.
First, in a general case, the adversaries would not be aware that the network is or is not protected, e.g., is using the dynamic limits algorithm.
As a result, adversaries would want to do as much harm as possible, which is to send junk Interests.

% Second, when adversary is aware of the attack mitigation mechanisms and sends 
Second, a satisfiable Interests does not cause NDN-specific harm, as they would not linger on routers for extended periods of time, giving opportunities for Interests from the legitimate users to get through and bring Data back.
Essentially, in the worst case scenario (assuming that dynamic limits are augmented with some form fair queuing), legitimate users and attackers would ``fairly'' share the network.
Note that router resource, as well as upstream link capacity overloading is still impossible, as there is always an upper bound of admitted Interets.

%  and the mitigation algorithm will work as expected: small service quality degradation during first seconds of the attack, followed by practically full recovery from the attack.
% However, a careful reader may ask a totally legitimate question: what would happen if adversaries know that the network is protected and know that it is using the dynamic limits algorithm?
% Would there be an optimal strategy to deny service for the legitimate users?
% Would it be better to send ``legitimate'' Interests instead, at least partially, and attempt to always keep the network in the transitional state?

>>>>

The attack mitigation methods studied in this paper provide ways to eliminate network congestion and router overload problems caused by junk Interest flooding (Section~\ref{sec:interest flooding}), but unfortunately not without inducing some new problems.
In particular, during an ongoing attack, a number of legitimate Interests successfully forwarded towards the Data producer can be substantially larger in unprotected network, then in the network that implements an Interest mitigation algorithm.  
This is simply because an unprotected network allows clients to pump more packets and does not impose any artificial restrictions on packet forwarding.
Therefore, unless a mitigation algorithm uses some form of intelligence (e.g., statistics for Interest satisfiability), a smaller scale flooding attack can cause greater damage to the service quality.
% (recall service quality curves for physical limits in small-scale and larger-scale evaluations, Fig.~\ref{fig:small-scale} and Fig.~\ref{fig:large-scale}).

@@

In the definition of the Interests flooding attack we explicitly stated that an attack is carried using junk Interets, which obviously gives us a clear distinction between ``good'' and ``bad'' Interests.
A curious reader may ask us a valid question: what would happen if an adversary doing something else, e.g., sending sends only ``legitimate'' Interests or intermix them with junk Interests?
Although a complete investigation of this problem deserves a separate study, we anticipate that the problem may not be as severe as it seems.
First, in a general case, the adversaries would not be aware that the network is or is not protected, e.g., is using the satisfaction-based pushback algorithm.
As a result, adversaries would want to do as much harm as possible, which is to send junk Interests.

% Second, when adversary is aware of the attack mitigation mechanisms and sends 
Second, a satisfiable Interests does not cause NDN-specific harm, as they would not linger on routers for extended periods of time, giving opportunities for Interests from the legitimate users to get through and bring Data back.
Essentially, in the worst case scenario (assuming that satisfaction-based pushback is augmented with some form fair queuing), legitimate users and attackers would ``fairly'' share the network.
Note that router resource, as well as upstream link capacity overloading is still impossible, as there is always an upper bound of admitted Interets.

%  and the mitigation algorithm will work as expected: small service quality degradation during first seconds of the attack, followed by practically full recovery from the attack.
% However, a careful reader may ask a totally legitimate question: what would happen if adversaries know that the network is protected and know that it is using the satisfaction-based pushback  algorithm?
% Would there be an optimal strategy to deny service for the legitimate users?
% Would it be better to send ``legitimate'' Interests instead, at least partially, and attempt to always keep the network in the transitional state?

### 2013-01-11 08-conclusion.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
The most effective of the designed algorithms---dynamic limits---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data pah symmetry and full receiver-based traffic control.
In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Intersets can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.

>>>>

In this paper we demonstrated that NDN architecture can be quite resilient against Interest flooding attacks, which aim to overwhelm network capacity as well as memory resources on NDN routers.
The most effective of the designed algorithms---satisfaction-based pushback---almost completely eliminates the attack (or at least mitigates it to an acceptable ``fair'' level), leveraging two key aspects: Interest/Data pah symmetry and full receiver-based traffic control.
In particular, it measures how well Interests are getting satisfied (path symmetry) and uses these measurements to adjust how many Intersets can be accepted from each individual interface (receiver-based control), effectively pushing the attack to the edges.

### 2013-01-11 eval-small-scale.tex
More renaming of algorithms
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@896 df1a90cd-247b-4364-bdaf-287a704eb499

\paragraph{\textbf{Simple token buckets}}

@@

Let us take a deeper look on what is happening with the physical limits algorithm.
Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as physical limits restricts the number of forwarded Intersets!).
This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
In this example we assume that both the legitimate user and the adversary send Interests in about the same time.

@@

The described problem arises from the clocking effect and can be solved in a number different ways.
Augmenting physical limits algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.

@@

The presented results demonstrate the overall, and somewhat obvious, trends for all attack mitigation algorithms: the larger is the attack, the lower service quality is observed by the legitimate users.
Physical limits with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for the satisfaction-based Interest accept method and less than by 10\% in the satisfaction-based pushback algorithm.

>>>>

\paragraph{\textbf{Simple token bucket}}

@@

Let us take a deeper look on what is happening with the simple token bucket algorithm.
Essentially, we observe an extremely successful denial of service attack, where attackers almost completely shut down legitimate users from the Data producer (using a relatively small amount of Interests, as token bucket restricts the number of forwarded Intersets!).
This ``success'' can be explained using a simplistic example, illustrated on Fig.~\ref{fig:three router example}, where each router has only one token for Interest forwarding.
In this example we assume that both the legitimate user and the adversary send Interests in about the same time.

@@

The described problem arises from the clocking effect and can be solved in a number different ways.
Augmenting token bucket algorithms with per-interface fair queueing allows us to eliminate the clocking effect. 
That is, in the second case when router A releases the token after the first ``lock out'' period, it will immediately process previously enqueued Interests from the legitimate user.
However, because the Interest time out (``lock out'' time) is most likely be larger than the time to actually fetch the Data, an adversary is still able to ``unfairly'' deny service to good guys.
Ideally, if there are only 40\% of compromised users, the rest good users should get at least 60\% of network resources, which is not true as can be seen on Fig.~\ref{fig:small-scale attack progress}.
We expect that reducing the maximum hold time for Interests (e.g., to an order of average RTT) would improve overall performance for legitimate users, with negative effect of requiring extra complexity for Intersets processing.

@@

The presented results demonstrate the overall, and somewhat obvious, trends for all attack mitigation algorithms: the larger is the attack, the lower service quality is observed by the legitimate users.
Token bucket algorithm with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for the satisfaction-based Interest accept method and less than by 10\% in the satisfaction-based pushback algorithm.
